Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-04-21 paper/paper.tex
i ==> 1, ii ==> 2, etc. in abstract

The present paper proposes a \textit{process model}
that tries to explain \textit{how}
the DMN may implement
continuous assessment and prediction of the environment to guide action choices.
%
DMN function is recast in mathematical terms of
control theory and reinforcement learning based on Markov decision processes.
%
We argue that our formal account of DMN function naturally accommodates as special cases
the previously proposed cognitive accounts on
\textit{i}) predictive coding,
\textit{ii}) semantic associations, and
\textit{iii}) a ``sentinel'' function.
%
A process model for the neural optimization of complex behavior in the DMN
offers parsimonious explanations for
various experimental findings in animals and humans.
\end{abstract}

>>>>

The present paper proposes a \textit{process model}
that tries to explain \textit{how}
the DMN may implement
continuous assessment and prediction of the environment to guide action choices.
%
DMN function is recast in mathematical terms of
control theory and reinforcement learning based on Markov decision processes.
%
We argue that our formal account of DMN function naturally accommodates as special cases
the previously proposed cognitive accounts on
(1) predictive coding,
(2) semantic associations, and
(2) a ``sentinel'' function.
%
A process model for the neural optimization of complex behavior in the DMN
offers parsimonious explanations for
various experimental findings in animals and humans.
\end{abstract}
